### 2024-05-31 paper-reviews/papers-2024.tex
Add Megatron-LM paper

    The paper proposes a class of hardware efficient Monarch matrices. The matrices are proposed as a replacement for dense weight matrices in order to reduce compute/memory requirements of large neural networks. Monarch matrices are block diagonal matrices that can represent many fast transforms such as Fourier or convolution. The authors show that dense-to-sparse conversion has an analytically optimal solution. A Monarch matrix is described by $2n\sqrt{n}$ parameters instead $n^2$ for dense matrix. Monarch parametrization allows efficient utilization of batch matrix multiply units available in contemporary hardware such as GPUs. The parametrization allows to achieve up to $2x$ speedup compared to dense matrix multiply. Algorithm proposed in the paper allows to fine-tune a pre-trained model into a model with Monarch weight matrices. The work presented in the paper is a step towards doing structural matrices more practical.
\end{itemize}

>>>>

    The paper proposes a class of hardware efficient Monarch matrices. The matrices are proposed as a replacement for dense weight matrices in order to reduce compute/memory requirements of large neural networks. Monarch matrices are block diagonal matrices that can represent many fast transforms such as Fourier or convolution. The authors show that dense-to-sparse conversion has an analytically optimal solution. A Monarch matrix is described by $2n\sqrt{n}$ parameters instead $n^2$ for dense matrix. Monarch parametrization allows efficient utilization of batch matrix multiply units available in contemporary hardware such as GPUs. The parametrization allows to achieve up to $2x$ speedup compared to dense matrix multiply. Algorithm proposed in the paper allows to fine-tune a pre-trained model into a model with Monarch weight matrices. The work presented in the paper is a step towards doing structural matrices more practical.

    \item \cite{Shoeybi:MegatronLM:2020}:

    The article describes techniques for training large transformer models that is based on intra-layer model parallel approach. The approach doesn't require a complier or library changes and is only based on PyTorch level changes to a model. The approach is demonstrated by increasing number of parameters for existing transformer models. The main idea of the technique is to partition GEMM in a way that allows non-linear functions to be applied to each partition independently. The technique is aimed to reduce number of communications (reductions) introduces py partitioning. The technique is orthogonal to data parallelism thus allowing combination of the two. The approach has demonstrated near linear scaling.
\end{itemize}
